### 2025-05-25 conteudo/methods/methods.tex
fix small typos on text

We employ a multi-method research approach, using different methodologies to achieve our goals
to approach code duplication in some of the Linux subsystems. 
To validate if the Arkanjo tool is capable of finding code duplications, 
applied two independent methods and perform triangulation on the results.

@@

The ethnographic study happened in two phases. 
In the first phase, the author of this research explored the process of mitigating
a code duplication found in the AMD Display Driver and sent it as a PATCH to iteract with the
Linux community and get their feedback. On a second phase, we proposed to students on the 
course Free Software Development at University São Paulo to mitigate the code duplications found 
by the tool in the IIO subsystems and the AMD Display Driver and pass the process of send the mitigations as PATCH.
(DOUBLE CHECK IF THE STUDENTS HAVE SENT THE PATCHES).

\todo[inline]{I SHOULD mention that the test on the tool were made using the gensim similarity method and not the git method.}

@@

\todo[inline]{I just mention the problem, maybe a more explictly mention of the problem here or on the background would be good.}

@@

\todo[inline]{Take care: Big focus on AMD display driver and the tone of the writing supports the focus. }

@@

\subsection{Research with students}

\todo[inline]{Research with students does not look good.}

@@

In the Free Software Development course at University of São Paulo, ministred by the advisor 
of this work at the first semester of 2025, we have proposed to the students the possibility
of mitigating duplications in the IIO subsystem and the AMD display driver found with the Arkanjo tool.
The course had a total of 26 students, and of that, X students being undergraduate students
and Y begin graduate students.

@@

For the first alternative, one of the teaching assistants used the Arkanjo tool in the IIO subsystem and
listed interesting duplicated functions pair that the groups can simple mitigate this specific duplication pair, 
and it is up to the students on how
to refactor the code to mitigate the duplications and pass through the process to send patches to the IIO 
maintainers to review. For the second alternative, we propose a similar experience then the 
participant observation method, where the students pass through the whole process of executing the Arkanjo tool
in the AMD display driver, analyze the duplications found, create a patch to mitigate a duplication and sent
the patch to the AMD display driver's maintainers.

@@

For the teaching assistant and the student that executed the Arkanjo tool to explore duplications, 
we have asked them to answer some questions related to the experience of using the tool and what could be
improved. The questions asked is the following:

>>>>

We employ a multi-method research approach, using different methodologies to achieve our goals
to approach code duplication in some of the Linux subsystems. 
To validate if the ArKanjo tool is capable of finding code duplications, 
applied two independent methods and perform triangulation on the results.

@@

The ethnographic study happened in two phases. 
In the first phase, the author of this research explored the process of mitigating
a code duplication found in the AMD Display Driver and sent it as a PATCH to iteract with the
Linux community and get their feedback. On a second phase, we proposed to students on the 
course Free Software Development at University São Paulo to mitigate the code duplications found 
by the tool in the IIO subsystems and the AMD Display Driver and pass the process of send the mitigations as PATCH.

@@

@@

@@

\subsection{Study with University Students}

@@

In the Free Software Development course at University of São Paulo, ministred by the advisor 
of this work at the first semester of 2025, we have proposed to the students the possibility
of mitigating duplications in the IIO subsystem and the AMD display driver found with the ArKanjo tool.
The course had a total of 26 students, and of that, X students being undergraduate students
and Y begin graduate students.

@@

For the first alternative, one of the teaching assistants used the ArKanjo tool in the IIO subsystem and
listed interesting duplicated functions pair that the groups can simple mitigate this specific duplication pair, 
and it is up to the students on how
to refactor the code to mitigate the duplications and pass through the process to send patches to the IIO 
maintainers to review. For the second alternative, we propose a similar experience then the 
participant observation method, where the students pass through the whole process of executing the ArKanjo tool
in the AMD display driver, analyze the duplications found, create a patch to mitigate a duplication and sent
the patch to the AMD display driver's maintainers.

@@

For the teaching assistant and the student that executed the ArKanjo tool to explore duplications, 
we have asked them to answer some questions related to the experience of using the tool and what could be
improved. The questions asked is the following:

### 2025-05-25 conteudo/tool/functionalities.tex
change tool figures
fix small typos on text

\begin{figure}
\includegraphics[scale=0.5]{explorer_example}
\caption{Example of the \textit{Duplication Explorer} functionality of the Arkanjo tool in action.}
\label{fig:explorer_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{function_example}
\caption{Example of the \textit{Function Information} functionality of the Arkanjo tool in action.}
\label{fig:function_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{relatory_example}
\caption{Example of the \textit{Duplication Report} functionality of the Arkanjo tool in action.}
\label{fig:relatory_ex}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.30]{explorer_example}
\caption{Example of the \textit{Duplication Explorer} functionality of the ArKanjo tool in action.}
\label{fig:explorer_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.3]{function_example}
\caption{Example of the \textit{Function Information} functionality of the ArKanjo tool in action.}
\label{fig:function_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.3]{relatory_example}
\caption{Example of the \textit{Duplication Report} functionality of the ArKanjo tool in action.}
\label{fig:relatory_ex}
\end{figure}

### 2025-05-25 conteudo/tool/tool.tex
fix small typos on text

Arkanjo, our proposed tool, is a Command Line Interface (CLI) application designed to
help developers identify code clone duplication at the function level.
Specifically, it enables the detection of pairs of functions within a codebase
that are clones of each other.

@@

The Arkanjo tool has been implemented and is available for reference at
\url{https://github.com/LipArcanjo/arkanjo}.

>>>>

ArKanjo, our proposed tool, is a Command Line Interface (CLI) application designed to
help developers identify code clone duplication at the function level.
Specifically, it enables the detection of pairs of functions within a codebase
that are clones of each other.

@@

The ArKanjo tool has been implemented and is available for reference at
\url{https://github.com/LipArcanjo/arkanjo}.
